General Comments

### 2023-07-30 third-submission/suggestions/deprecated/2023-may.tex

\begin{document}
\title{AE Comments}
\author{}
\date{}
\maketitle

%\begin{enumerate}
%\item I would revert back to the original notation as I find the A, B to be confusing and it's not easy to extend to multiple files. (See Aleshin-Guendel (2022) for reference. I'm not sure what Jerry thinks about this though. Typically changes should be agreed upon by all authors or some standard.
%\item Perhaps to make things easy on you, I can propose some changes in the document and help and iterate and then we can ask Jerry regarding his opinions regarding this. 
%\item Let us also make a plan for outlining your thesis and a schedule so it can move ahead. Would you like suggestions or to propose something yourself? 
%\end{enumerate}

\section{AE Comments with responses}

@@

Note: I do not believe that we should be integrating out the prior distribution. I think we did this at the confusion from the first revision of the  AE. We should instead just update the conditionals to form a Gibbs update, which will make the algorithm justified. If you believe that the algorithm is correct, we will need to convince the AE why it is a valid Markov chain or rather Gibbs update of the partition. 

@@

\textcolor{blue}{It will not be justified unless the full conditionals of the Gibbs sampler contain a sequential update or one proves that this is a justified Gibbs sampler. This was the point that Serge mentioned in his email. Currently, it is not a valid Gibbs sampler. I attempt to explain this more clearly below. Looking at Pitman, Pruenster, and the BNP literature, I cannot find a reference regarding why the Markov chain would be valid in this case. If you were to prove this, it would be a new result (to my knowledge).}

It would need to be something like this, which comes from Aleshin-Guendel and Steorts (2023), which extends the general clustering literature. The partition is equivalent to the co-reference matrix or linkage structure. The partition approach is more widely understood by the Bayesian non-parametrics community (or statistics community), which is why we are using this terminology. (They will not easily understand the linkage structure or coreference matrix without connections being made for them).

@@

\end{quote}
\item Sections 4.1 and 4.2 (I have gone through this, however, I suggest that we all go through this many times and write out responses very clearly). I am doing my best to get through this as quickly as possible and make recommendations.  
\end{enumerate}

>>>>

\begin{document}
\title{General Comments}
\author{}
\date{}
\maketitle

\section{Suggestions}

\begin{enumerate}
\item Let us read through the paper extremely carefully (everyone, including myself and Jerry) to make recommendations and formulate a plan. 
\item I think it would be helpful to make comments outside the main document before making major changes in the document to make sure we address everything and check that we address every comment that was made by the Editor/AE. 
\item Should try and make clear and crisp answers to them (and cite existing literature to avoid opening any holes or new issues). 
\item I will do my best to serve as a "reviewer/editor" and find other comments to fix. 
\item If you find yourself getting frustrated, etc. please reach out/let me know. One idea is to work on another project that might be more fun or start formulating the rest of your thesis in case this might be weighing you down. I'd be happy to sketch this out with you and help you as much as you might like, Brian.
\end{enumerate}

\section{General Comments}

\begin{enumerate}
\item The connection between the relaxation of Sadinle (2018) of the bipartite linkage structure may be getting lost due to AE comment 3 as they stated ``they surprised me" regarding how the fabl prior was defined. This should be looked at more carefully and introduced with more care regarding the contribution of the prior as a generative (Bayesian) prior with post-processing after due to the computational issues faced with that of Sadinle. (This is AE comment 3). 
\item Section 2 could be structured to be more clear to a general reader regarding notation overall, prior work (FS and Sadinle) and then the relaxation of the Sadinle (2018) prior. (Editor comment). 
\item The overall paper needs extensive checking regarding consistent notation, consistent a, no repetitive comments, no typos, etc. (Editor comment). 
\item Appendix 8.2 needs to be provided without any typos and all details provided. (Don't skip any steps and do not use any short hand notation). I think that this was the main point of confusion for the reviewer. You may wish to refer to Aleshin and Guendel and Sadinle (2022) and follow their notation as it appears this may be what you want. See Appendix B.2 page 27. (In short, they use the notation $\mathcal{L}_{ij}$ to make it clear that this is a factor coming from the likelihood). I think that you could make your proof more clear for those working on this topic, which make this an opportunity and opening as it wasn't clear to the AE (and it's probably not obvious to others).
\item Let's walk through each part of AE comment 3. I think it would be helpful to refer to Appendix B.2 of Aleshin and Guendel and Sadinle (2022) regarding this discussion. Page 25--26.

``Thank you for including the details on integrating out pi from the full conditionals. They surprised me. I had assumed that the authors had integrated out pi in the prior for Z as this is what Sadinle (2017) had done to form the "beta prior for bipartite matchings."

``Does the alternate approach presented in this paper provide a different algorithm than directly integrating the prior distribution."

\textcolor{blue}{Yes, as mentioned, our approach is a relaxation of that of Sadinle (2017) as we relax the one-to-one assumption. Our algorithm provided is not the same, however, empirically we find the the results are similar due to a pre-processing step that has been utilized in the literature by Jaro (??).}

``Is the presented algorithm justified?"

\textcolor{blue}{It will not be justified unless the full conditionals of the Gibbs sampler contain a sequential update or one proves that this is a justified Gibbs sampler. This was the point that Serge mentioned in his email. Currently, it is not a valid Gibbs sampler.}

It would need to be something like this, which comes from Aleshin-Guendel and Steorts (2023). The partition is equivalent to the co-reference matrix or linkage structure. The partition approach is more widely understood by the Bayesian non-parametrics community (or statistics community), which is why we are using this terminology. (They will not easily understand the linkage structure or coreference matrix without connections being made for them).

\end{quote}

\item I have comments about the hashing section, which are largely that I think the AE/Editors are having a difficult time with this section. I think their main concerns are with the following \textbf{notation, precise wording, understanding of the paper, correctness of the appendix}. I would suggest that we all carefully read through the paper and have a plan, where we are all on the same page regarding our response and revisions.

%Is it not the case that in the setup, one does not need to integrate out $\pi.$ In short, one can write
%\begin{align}
%P(Z, \Phi \mid \pi, \gamma_{obs}) \propto L(Z, \Phi \mid \gamma_{obs}) P(\Phi \mid \gamma_{obs}) P(Z \mid \pi) P(\pi)
%\end{align}
\end{enumerate}

\section{Language/Writing}
\begin{enumerate}
\item There is repetition present in the manuscript, such as the first two lines of the opening paragraph of the introduction. For example, analysis, analysts, and analyses are used three times in the first two sentences. Tasks is used twice. Furthermore, the language could be written to be more precise and condensed. ``In many applications, users seeks to identify duplications across two data files." (This removes the repetition, and I think the remainder can stay). 
\item This should be checked in an editor checked such as Antidote closer to the time of resubmission. 
\end{enumerate}

\section{Notation}

\begin{enumerate}
\item The notation is not clear or consistent throughout. 
\item The notation is confusing at times when reading through the paper, where one has to flip back and forth between pages to re-reference previously defined notation. The authors should more carefully define (perhaps following that of Sadinle (2018) to avoid typos) and use referencing of equations so that the reader doesn't have to constantly flip back and forth throughout the manuscript. 
\item The usage of lower and upper case greek letters should be consistent. The usage of subscripts should be consistent. It appears that Sadinle (2018) and Aleshin and Guendel and Sadinle (2022) make use of notation consistently, so this could be followed. It might be worth noting that they utilize $X_1$ and $X_2$ in order to more effectively extend to any number of databases, so this might be more natural than $A$ and $B.$ 
\end{enumerate}

\newpage
\section{AE Comments with responses}

@@

Note: I do not believe that we should be integrating out the prior distribution. I think we did this at the confusion from the first revision of the  AR. We should instead just update the conditionals to form a Gibbs update, which will make the algorithm justified. If you believe that the algorithm is correct, we will need to convince the AE why it is a valid Markov chain or rather Gibbs update of the partition. 

@@

\textcolor{blue}{It will not be justified unless the full conditionals of the Gibbs sampler contain a sequential update or one proves that this is a justified Gibbs sampler. This was the point that Serge mentioned in his email. Currently, it is not a valid Gibbs sampler. I attempt to explain this more clearly below.}

It would need to be something like this, which comes from Aleshin-Guendel and Steorts (2023). The partition is equivalent to the co-reference matrix or linkage structure. The partition approach is more widely understood by the Bayesian non-parametrics community (or statistics community), which is why we are using this terminology. (They will not easily understand the linkage structure or coreference matrix without connections being made for them).

@@

\end{quote}

\end{enumerate}
